---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
---
title: "Case Study 3 - Patterns and Trends of Customer Behavior"
author: "DarkAstronaut"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
### Aim
  The aim of this case study is to find how a Customer acts (Purchases made by the customer) and to gain an insight on the type of the purchases made on an online platform in various countries. 

### Data
```{r FirstSteps, include= FALSE}
setwd("C:/Users/vk0589/OneDrive - UNT System/Documents/UNT/INFO_5307/Datasets")
#install.packages("tidyverse")
library(readxl)
data1 <- read_excel("OnlineRetail.xlsx")
data2 <- as.data.frame(data1)
```
We use the dataset **OnlineRetail.xlsx** (Source: Kaggle). The data is in a Excel Workbook (XLSX) File with 8 Attributes and 541909 Observations. The attributes are:
```{r ColNames,echo = FALSE, message= FALSE}
names(data2)
```
<!--and the sample data is:
```{r SampleData,echo = FALSE, message= FALSE}
head(data2)
```
-->
Instead of working on the complete data, we will take few countries from the below mentioned list
```{r CountryList, echo=FALSE, message=FALSE}
print(levels(as.factor(data2$Country)))
```
The Countries that I would be working on are:
- USA
- Japan
- 
- 



